\documentclass[letterpaper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}
\usepackage{fontawesome}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Rajdeep Gill} \\ \vspace{1pt}
    \small 431-998-9785 $|$ \href{mailto:hi.rajdeepgill@gmail.com}{\underline{hi.rajdeepgill@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/rajdeep-gill-4ab365220}{\underline{linkedin.com/in/rajdeep-gill-4ab365220}} $|$
    \href{https://github.com/Rajdeep-Gill}{\underline{github.com/Rajdeep-Gill}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {University of Manitoba}{Winnipeg, MB}
      {Bachelor of Science in Computer Engineering}{Sept. 2021 - May 2026}
      \begin{itemize}
          \item \small{GPA: \textit{4.45/4.5}}
          \item \small{Relavent Coursework: \textit{Engineering Algorithms, Data structures and Algorithms, Systems Engineering Principles}}
      \end{itemize}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading{Undergraduate Research Student}{May 2024 - August 2024}{University of Manitoba - Biosensors Research Lab}{Winnipeg, MB}
		\resumeItemListStart
      \resumeItem{Designed and trained a neural network to predict biological cell viability from cell diffraction patterns, achieving an accuracy of 85\%, demonstrating the feasibility of non-invasive cell viability prediction.}
      \resumeItem{Enhanced particle diffraction centroid detection using computer vision, boosting success rate from 75\% to 92\%, allowing for better statistical analysis.}
      \resumeItem{Developed an interactive interface for data analysis, allowing for real time visualization of diffraction patterns.}
		\resumeItemListEnd

    \resumeSubheading{Undergraduate Research Student}{May 2023 - August 2023}{University of Manitoba - Biosensors Research Lab}{Winnipeg, MB}
		\resumeItemListStart
			\resumeItem{Employed dimensionality reduction techniques, including t-SNE and principal component analysis to compare and cluster datasets, identifying potential correlations and directing future research directions.}
			\resumeItem{Utilized parallel processing to reduce run times, enhancing research team productivity.}
      \resumeItem{Streamlined data collection for a seperate lab project by developing a program to interface with an oscilloscope.}
		\resumeItemListEnd
      

% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
         \resumeProjectHeading{{\textbf{Discord Clone}} $|$ \emph{React, TypeScript, HTML/CSS, Next.js}}{}
			\resumeItemListStart
				\resumeItem{Developed a feature-rich Discord Clone with real-time messaging using web sockets.}
        \resumeItem{Utilized Tailwind CSS to create a visually appealign and responsive user interface.}
        \resumeItem{Implemented API services to handle user authentication, voice and video calls.}
				\resumeItem{Provided users with extensive control, allowing them to edit and delete messages, create and delete servers.}
			\resumeItemListEnd

          \resumeProjectHeading{\textbf{Microprocessor Communication System} $|$ \emph{C, Java}}{}
        \resumeItemListStart
          \resumeItem{Designed and implemented a server using the TCP/IP stack in C, handling multiple concurrent connections.}
          \resumeItem{Developed a Java-based proxy server to interface between an Android application and the microprocessor server.}
          \resumeItem{Designed the Android application to allow users to control the LEDs, monitor the temprature and button states of the microprocessor.}
        \resumeItemListEnd

        \resumeProjectHeading{{\textbf{Chess Game}} $|$ \emph{Python}}{}
          	\resumeItemListStart
            	\resumeItem{Created a command line chess game using Python.}
            	\resumeItem{Implemented features such as move validation, checkmate detection, and piece promotion.}
            	\resumeItem{Currently developing multiplayer functionality to enable real-time play between users.}
          	\resumeItemListEnd

		
    \resumeSubHeadingListEnd

    

%--------------AWARDS--------------
\section{Awards}
    \resumeSubHeadingListStart
        \resumeProjectHeading
            {{\textbf{NSERC Undergraduate Student Research Award}}{}}{2023, 2024}
        \resumeProjectHeading
            {\textbf{Presidents Scholarship}\emph{}}{2021-2024}
    \resumeSubHeadingListEnd
%-------------------------------------------

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
		\textbf{Languages}{: Python, Java, C, JavaScript, HTML/CSS, R} \\
		\textbf{Frameworks}{: React} \\
		\textbf{Developer Tools}{: Git, VS Code, Visual Studio, Android Studio, IntelliJ} \\
    }}
 \end{itemize}
%-------------------------------------------

\end{document}
