\documentclass[11pt]{article}
\usepackage[T1]{fontenc}
\usepackage{lmodern}

%\usepackage[scale=.9]{lmodern} % or helvet
\renewcommand{\familydefault}{\sfdefault}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{listings}
\usepackage{tabularx}
\usepackage{xcolor}
\input{glyphtounicode}

%///////////////////////////////%
%----SPEEMCH'S RESUME TEMPLATE----%
%///////////////////////////////%

%----------FONT OPTIONS----------

% sans serif font -  lmss is recommended
% serif font - cmr is recommended
% ctrl-f and replace one with the other 


% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-0.6in}
\addtolength{\textheight}{1.3in}
\addtolength{\footskip}{-0.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{-1.5em}

% \definecolor{burntorange}{HTML}{BF5700}
\definecolor{burntorange}{HTML}{000000}
% Sections formatting
\titleformat{\section}{\color{burntorange}\vspace{-10pt}\scshape\raggedright\large\bfseries}{}{0em}{}[\vspace{-1pt} \color{burntorange}\titlerule \vspace{-6pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {\fontfamily{lmss}#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
     {\fontfamily{lmss} \textbf{#1} & #2 \\[-1.6pt]
      \textit{\small#3} & \textit{\small #4} \\}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingInline}[3]{
  \vspace{2pt}\item
  \begin{tabular*}{0.95\textwidth}[t]{l@{\extracolsep{\fill}}r}
    \hspace{1.2em}\textbf{#1} \textit{\small #3} & #2
  \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingUpd}[4]{
  \vspace{2pt}\item
    \begin{tabular*}{0.95\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \hspace{1.2em}\textbf{#1} & {\bfseries #2} \\
      \hspace{1.25em}\textit{\small#3} & \textit{\small#4}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      {\fontfamily{lmss}\textit{\small#1} & \textit{\small #2} \\}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
     {\fontfamily{lmss} \small#1 & #2 \\}
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{\fontfamily{lmss}$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------




\begin{document}
\fontfamily{lmss} %FONT HERE
\vspace{-1em}
\begin{center}
    \textbf{\LARGE\scshape Rajdeep Gill}\\ 
    \small 431-998-9785 $|$ \href{hi.rajdeepgill@gmail.com}{\underline{hi.rajdeepgill@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/gill-rajdeep/}{\underline{LinkedIn}} $|$
    \href{https://github.com/rajdeep-gill}{\underline{GitHub}} $|$
    Canadian Citizen\\
\end{center}
\vspace{-1.5em}
%-----------EDUCATION-----------
\section{Education}
    \resumeSubHeadingListStart
    \resumeSubheadingInline
      {University of Manitoba}{May 2026}{}
    \vspace{-0.4em}
  \resumeSubHeadingListEnd
  %\begin{itemize}[leftmargin=0.15in, label={}]
    \small{{\quad B.S. Computer Engineering}\hfill {\textbf{4.46/4.5 GPA}}
    \vspace{0.1em}\\
    {\quad Coursework: Data Structures and Algorithms, Parallel Computing, Digital Signal Processing}}
  %\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheadingUpd{Robinhood}{May 2025 - Sept 2025}{Software Engineer Intern}{Toronto, ON}
      \vspace{0.3em}
      \resumeItemListStart
        \resumeItem{Working on creating a dashboard to visualize and handle margin calls and liquidations for Robinhood's brokerage team.}
        \resumeItem{Implementing integration tests to ensure the reliability of the dashboard, and working on improving the performance of the dashboard by optimizing the data fetching and processing.}
        %\resumeItem{Bullet Point 2 - Accomplished X (deliverable) as measured by Y (metrics) by doing Z (technical/impl. details).}
        %\resumeItem{Bullet Point 3 - Accomplished X (deliverable) as measured by Y (metrics) by doing Z (technical/impl. details).}
      \resumeItemListEnd

    \resumeSubheadingUpd{Biosensors Research Lab}{May 2024 - Dec 2024}{Undergraduate Research Student}{Winnipeg, MB}
      \vspace{0.3em}
      \resumeItemListStart
        \resumeItem{Developed and trained a CNN to predict health of cells based on scattering images, achieving 85\% accuracy.}
        \resumeItem{Created a data visualization tool to display cell health data based on the model's predictions.}
        \resumeItem{Improved parameter extraction by 17\% with a custom centroid detection algorithm, making use of dynamic thresholding and edge detection.}
        \resumeItem{Developed a data extraction pipeline with OpenCV and parallelizing with OpenMP, reducing processing time by 40\%.}
        \resumeItem{Built a SQL database to store experimental data and processed results, along with a REST API to query the data.}
      \resumeItemListEnd

    \resumeSubheadingUpd{Biosensors Research Lab}{May 2023 - Aug 2023}{Undergraduate Research Student}{Winnipeg, MB}
      \vspace{0.3em}
      \resumeItemListStart
        \resumeItem{Developed an automated oscilliscope testing platform with PyVISA to streamline data collection, reducing manual collection time and ensuring repeatability.}
        \resumeItem{Optimized existing data analysis algorithms with vectorization and parallelization, reducing processing time by 90\%.}
        \resumeItem{Explored the use of unsupervised learning to cluster data points based on their impedance spectra.}
        \resumeItem{Implemented a prediction model based on a Gaussian Mixture Model and probabilistic neural networks to predict the health of cells based on their impedance spectra.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

  \vspace{-0.5em}
%-----------------PROJECTS------------------

\section{Projects}
\resumeSubHeadingListStart

%-----------ACTIVITIES-----------
%\vspace{0pt}\section{Activities}
    %\resumeSubHeadingListStart

    %\resumeSubheadingInline{Student Organization}{}{Member}
    %\vspace{0.2em}
    %    \resumeItemListStart
    %    \resumeItem{Bullet Point 1.}
    %    \resumeItem{Bullet Point 2.}
    %  \resumeItemListEnd
    %\resumeSubHeadingListEnd
    
    \resumeSubheadingInline{Distributed Image Processing}{}{(C++, OpenMPI)}
    \vspace{0.2em}
        \resumeItemListStart
            \resumeItem{Created a distributed image processing tool to process large images across multiple nodes, achieving a 95\% efficiency.}
            \resumeItem{Implemented a custom communication protocol to optimize data transfer latency and throughput.}
            \resumeItem{Utilized OpenMPI to handle the distribution of tasks across multiple nodes, ensuring scalability and reliability.}
        \resumeItemListEnd

    \resumeSubheadingInline{Collaborative Document Editor}{}{(React, TypeScript, Socket.io, Flask)}
    \vspace{0.2em}
        \resumeItemListStart
        \resumeItem{Built a collaborative document editor enabling real-time multi-user editing and communication.}
        \resumeItem{Implemented bidirectional messaging with Socket.io for seamless updates, and developed a RESTful API using Flask.}
        \resumeItem{Enhanced user experience by integrating autocomplete and in-line suggestions powered by Google's Gemini API.}
      \resumeItemListEnd

    \resumeSubheadingInline{Financial Dashboard}{}{(React, TypeScript, Hono, PostgreSQL)}
    \vspace{0.2em}
        \resumeItemListStart
            \resumeItem{Developed a financial dashboard to visualize financial data, allowing users to track their investments and expenses.}
            \resumeItem{Utilized Hono to create a REST API to fetch and store financial data, and PostgreSQL to store the data.}
            \resumeItem{Implemented React to create a user-friendly interface, allowing users to visualize their financial data.}
        \resumeItemListEnd

    \resumeSubheadingInline{Interpretor}{}{(C++)}
    \vspace{0.2em}
        \resumeItemListStart
            \resumeItem{Developed an interpretor for a custom language to allow users to write and run code in a terminal.}
            \resumeItem{Implemented a lexer and parser to tokenize and parse the code, and a semantic analyzer to check for errors.}
        \resumeItemListEnd
    \resumeSubheadingInline{Network Simulator}{}{(Java)}
    \vspace{0.2em}
        \resumeItemListStart
            \resumeItem{Developed a network simulator with packet loss, congestion and corruption to test various protocols.}
            \resumeItem{Implemented Alternate Bit, Go-Back N, Selective Repeat and TCP to test under various conditions.}
        \resumeItemListEnd
    

    

    \resumeSubHeadingListEnd
\vspace{-1em}

%-----------PROGRAMMING SKILLS-----------
\section{Skills}
    \quad\small{\textbf{Programming Languages}: C++, Python, TypeScript, JavaScript, Java}\\\vspace{0.2em}
    \quad\small{\textbf{Frameworks and Libraries:} React, NextJS, PyTorch, OpenMPI}\\\vspace{0.2em}
    \quad\small{\textbf{Tools:} Git, Docker, PostgreSQL}\\\vspace{0.2em}
    \quad\small{\textbf{Concepts:} Backend/Frontend Development, Machine Learning, Networking, CI/CD, Microservices, Agile}
%-------------------------------------------
\end{document}
